### 2014-02-27 paper/retrofit.tex
grammar for blue Sigma
minor

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit
ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
       |  fork ie | send ie ie ie | ix1, ix2 <= recv. ie ie
iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE | fork iE 
       |  send iE ie ie | send iv iE ie | send iv iv iE
       |  ix1, ix2 <= recv. ie ie
io   ::=  (il, id ie)
Q    ::=  nil | io , Q
\end{code}

@@

\begin{figure}
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))| \\
  &|erase il (tconf id il' ie) =| \begin{cases}
    %|lconf bullet bullet bullet bullet| & |il' cantFlowTo il| \\
    |bullet| & |il' cantFlowTo il| \\
    |tconf id il' ie| & \text{otherwise}
  \end{cases} \\
  &|erase il (iS [id mapsto Q]) =| \begin{cases}
    |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
    & \text{the label of thread |id|} \\
    |(erase il iS) [id mapsto (erase il Q)]| & \text{otherwise}
  \end{cases} \\
  &|erase il Q = filter il Q|
\end{align*}
\caption{
Erasure function for configurations, threads, system state, and
message queus.  In all other cases, |erasef il| is applied
homomorphically.
\label{fig:erasure}
}
\end{figure}

@@

\begin{figure}
  Concurrent, round robin:
\begin{code}
  sched S (it1, it2, ldots)  = it2, ldots, it1
  sched D (it1, it2, ldots)  = it2, ldots
  sched N (it1, it2, ldots)  = it2, ldots
  sched F (it1, it2, ldots)  = it2, ldots, it1
\end{code}
  Sequential:
\begin{code}
  sched S (it1, it2, ldots)        = it1, it2, ldots
  sched N (it1, it2, ldots)        = it1, it2, ldots
  sched D (it1, it2, ldots)        = it2, ldots
  sched F (it1, it2, ldots, itn)   = itn, it1, it2, ldots
\end{code}
\caption{Scheduling policies}
\end{figure}

>>>>

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit
ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
       |  fork ie | send ie ie ie | ix1, ix2 <= recv. ie ie
iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE | fork iE 
       |  send iE ie ie | send iv iE ie | send iv iv iE
       |  ix1, ix2 <= recv. ie ie
io   ::=  (il, id ie)
Q    ::=  nil | io , Q
iS   ::=  emptyset | iS [ id mapsto Q ]
\end{code}

@@

\begin{figure}
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))| \\
  &|erase il (tconf id il' ie) =| \begin{cases}
    %|lconf bullet bullet bullet bullet| & |il' cantFlowTo il| \\
    |bullet| & |il' cantFlowTo il| \\
    |tconf id il' ie| & \text{otherwise}
  \end{cases} \\
  &|erase il emptyset = emptyset|\\
  &|erase il (iS [id mapsto Q]) =| \begin{cases}
    |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
    & \text{the label of thread |id|} \\
    |(erase il iS) [id mapsto (erase il Q)]| & \text{otherwise}
  \end{cases} \\
  &|erase il Q = filter il Q|
\end{align*}
\caption{
Erasure function for configurations, threads, system state, and
message queus.  In all other cases, |erasef il| is applied
homomorphically.
\label{fig:erasure}
}
\end{figure}

@@

\begin{figure}
  Concurrent, round robin:
\begin{code}
  sched step (it1, it2, ldots)  = it2, ldots, it1
  sched D (it1, it2, ldots)     = it2, ldots
  sched N (it1, it2, ldots)     = it2, ldots
  sched F (it1, it2, ldots)     = it2, ldots, it1
\end{code}
  Sequential:
\begin{code}
  sched step (it1, it2, ldots)     = it1, it2, ldots
  sched N (it1, it2, ldots)        = it1, it2, ldots
  sched D (it)                     = it
  sched D (it1, it2, ldots)        = it2, ldots
  sched F (it1, it2, ldots, itn)   = itn, it1, it2, ldots
\end{code}
\caption{Scheduling policies}
\end{figure}
